---
title: "Chiaramonte_week 8"
author: "Chiaramonte"
date: "2024-07-18"
output: html_document
---
 Writ a function for them in R that converts temperature from Celsius to Fahrenheit so that they can stop bothering you to do the conversion for them. Note that last week you converted F to C and this week is the opposite!
1A. In a code chunk, convert 22°C into Fahrenheit. Feel free to Google the formula. Also, note that you may want to be careful to use parentheses to make sure the order of operations is correct.
```{r Q1a}
22*(9/5)+32

```

```{r setup, Q 1b}
C_temp<- 22
C_temp*(9/5)+32

 
```  
Use R’s function syntax to make your scripted formula into a working function. Define the function (i.e., assign it to an object) in a code chunk.


```{r Q1c}
temp_conv<- function(celsius){
  
  math<-celsius*(9/5)+32
  return(math)
  
  
}
```

Use your new custom function to convert 5°C and 35°C into their equivalents in Fahrenheit in a final code chunk


```{r Q1D}

temp_conv(5)
temp_conv(35)

```